### 2018-03-16 chapter2/ms.tex
Fixed most figures/tables. Table 5.3 still busted.

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f1.pdf}
\caption{Top: Kilonova spectra from \citet{BarnesKasen13} at $\sim$ 1 d and $\sim$ 1 week with ejecta properties of $\Mej =10^{-2}\;M_{\odot}$ and $\beta_{\text{ej}} = 0.2$. Bottom: Light curve for the same model parameters computed at a fiducial distance of 200 Mpc in the DECam {\em r}, {\em i}- and {\em z}-band filters. \vspace{10pt}}
\label{fig:ch2_kilosample}
\end{figure}

@@

\clearpage
\begin{figure}[h!]
\centering
\includegraphics[width=0.65\textwidth]{./figs/chapter2/ch2_f2.pdf}
\caption{Top: {\em i}-band light curves of the contaminants considered in this work at a fiducial distance of 200 Mpc. Bottom: {\em z}-band light curves. See \cref{sec:ch2_WDmerge,sec:ch2_AIC,sec:ch2_ELDD,sec:ch2_type.Ia,sec:ch2_PSFast,sec:ch2_typeIa} for details.}
\label{fig:ch2_LCcont}
\end{figure}

@@

\clearpage
\begin{deluxetable}{cccccc}
\tabletypesize{\footnotesize}
\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Expected Rates For Fast Transients}
\tablehead{
\colhead{Object}&  \colhead{$\mathcal{R}_{\rm vol}$}& \colhead{$z_{\rm max}$}  &  \colhead{$\mathcal{R}_{\rm area}$} &  \colhead{$N$}     &     \colhead{Reference}      \\
\colhead{} & \colhead{(Mpc$^{-3}$ yr$^{-1}$)} & \colhead{} & \colhead{(deg$^{-2}$ yr$^{-1}$)} &  \colhead{} & \colhead{} }
\startdata
 Type .Ia    &                  10$^{-6}$                   &  0.5        &  $0.7$            &         1.4  & \citet{Bildsten+07} \\
 WD-NS mergers  &                  10$^{-5}$                   &   0.06        & $2\times10^{-2}$              &         $3\times10^{-2}$  &     \citet{Thompson+09}     \\
 WD-BH mergers  &      10$^{-5}$                   &    0.06        &   $2\times10^{-2}$              &      $3\times10^{-2}$  &    \citet{Fryer+99}          \\
AIC       &                  10$^{-6}$                   & 0.06        & $2\times10^{-3}$            &        $3\times10^{-3}$ &  \citet{Darbha+10}   \\
ELDD      &                  3$\times 10^{-7}$                   & 0.14        &    $6\times10^{-3}$           &      $1\times10^{-2}$ &  $\cdots$  \\
Pan-STARRS fast &                  5$\times 10^{-6}$                   &     0.5        &   $3.5$            &     7 &   \citet{Drout+14}
\enddata
\tablecomments{Expected rates for the various contaminants considered in \cref{sec:ch2_contaminants}. $\mathcal{R}_{\rm area}$ is computed assuming an isotropic distribution of sources in a volume defined by the comoving volume at $z_{\rm max}$.  The column $N$ refers to the number of events expected during a search covering 100 deg$^2$ for 7 days. See \cref{sec:ch2_rates} or details.}
\label{tab:ch2_rates}
\end{deluxetable}

@@

\clearpage
To estimate the expected number of events observed during a GW optical follow-up search we compute the number of sources per square degree per year. This is done by determining the maximum redshift to which the object can be observed to a limiting magnitude of $z \approx$ 23 mag (see \cref{sec:ch2_kilo,sec:ch2_MCsims_det}). This rate is then multiplied by the search area $(A \sim 100$ deg$^2$) and duration to get the number of expected sources for our observations. We compute the duration by assuming that a kilonova will be detected within approximately one day of the GW trigger. Therefore, we do not consider events that begin more than +2 d into the search. However, we do consider sources that begin up to twice their characteristic timescale ($\sim5$ d for rapid transients and $\sim 20$ d for Type Ia SNe) prior to the GW trigger, as they may remain visible when the search begins. The total duration is then 7 d for rapid transients and 22 d for Type Ia SNe. The number of expected sources is given in \cref{tab:ch2_rates,tab:ch2_rates_Iae}. Type Ia SNe dominate the number of expected events with $N \sim 568$ when summing across all redshift bins. Of the population of fast transients, only type .Ia and the Pan-STARRS fast transients are expected to have $N \gtrsim 1$. Despite the low expected occurrence rate for other fast transients, we still consider these sources in this analysis due to the large uncertainty in their rates.

@@

\begin{figure*}[t!]
\centering
\includegraphics[trim= 0 0 0 250 ,clip,width=\textwidth]{./figs/chapter2/ch2_f3.pdf}
\caption{Time-color (left) and time-magnitude (right) slices of the time-color-magnitude phase-space at a selection of redshifts. Arrow markers denote upper limits on the rise time. Note that in all panels the population of kilonovae are kept at the fiducial distance of $\sim$ 200 Mpc while redshift corrections are applied to the contaminant population. Kilonovae are well separated from the contaminant population in both color and timescales. The delineation in magnitude is less apparent.}
\label{fig:ch2_phase}
\end{figure*}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f4.pdf}
\caption{Depth versus start time grid in $r$ (top), $i$ (middle), and $z$ (bottom) for the four observing strategies. The contours indicate the fraction of sources detected in at least three epochs (25\% blue, 50\% cyan, 75\% yellow, 95\% red). The dashed lines represent the approximate 5$\sigma$ limiting magnitudes of several wide-field telescopes assuming the appropriate number of pointings necessary to cover a $\sim 100$ deg$^2$ error region with the required cadence. The choice of observing strategy does not drastically affect the fraction of sources detected at a given depth. We note that the early time drop in efficiency for {\em z}-band utilizing Strategy 2 is the result of the initial observations occurring before the light curve has brightened above the limiting magnitude.}
\label{fig:ch2_det}
\end{figure}

@@

\clearpage
\begin{deluxetable}{ccccc|cccc}
\tabletypesize{\footnotesize}
\tablecolumns{9}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Required 5$\sigma$ Limiting Magnitudes for Kilonova Detection}
\tablehead{\colhead{Filter} & \multicolumn{4}{c|}{With Pre-Existing Template} & \multicolumn{4}{c}{Without Pre-Existing Template} \\
\colhead{} & \colhead{Strategy \#1} & \colhead{Strategy \#2} & \colhead{Strategy \#3} & \multicolumn{1}{c|}{Strategy \#4} & \colhead{Strategy \#1} & \colhead{Strategy \#2} & \colhead{Strategy \#3} & \colhead{Strategy \#4}}
\startdata
$r$ & 24.9 (25.9) & 25.0 (25.9) & 24.5 (25.5) & 24.5 (25.5) & 25.0 (25.9) & 25.0 (25.9) & 25.0 (25.9) & 25.1 (25.9) \\
$i$ & 23.2 (23.9) & 23.3 (24.0) & 22.9 (23.9) & 22.9 (23.9) & 24.0 (24.9) & 24.3 (25.0) & 24.0 (24.9) & 24.3 (25.0) \\
$z$ & 22.2 (22.9) & 22.4 (23.2) & 22.1 (22.9) & 22.1 (23.0) & 23.1 (23.9) & 23.2 (24.0) & 23.1 (23.9) & 23.5 (24.2)
\enddata
\tablecomments{\,Limiting magnitudes $(5\sigma)$ required to detect 50\% (95\%) of kilonovae as a function of observing strategy and filter (\cref{sec:ch2_MCsims_det}, \Cref{fig:ch2_det}). Values are averaged over all start times. We compute the required depths for follow-up observations with and without a pre-existing template (\cref{sec:ch2_diff}).}
\label{tab:ch2_det}
\end{deluxetable}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f5.pdf}
\caption{Same as \Cref{fig:ch2_det}, except that the contours show the fraction of events for which a brightening is detected. The choice of observing strategy, start time, and filter have a strong impact on the detection of brightening.}
\label{fig:ch2_rise}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f6.pdf}
\caption{Probability density of kilonovae as a function of the change in brightness between the first and second observation $(\Delta m_21)$ versus the brightness in the second observation $(m_2)$ for each of the four observing strategies. The hatched region indicates the $2\sigma$ photometric error for DECam for an exposure time necessary to achieve the required depth. Points within this region will not exhibit a statistically significant change in magnitude for detection. The fraction of sources brighter than the detection limit in all three observations (DF) and the fraction of sources within the hatched region (missed) are indicated at the bottom of each panel. We find that the seemingly beneficial initial rapid cadence of Strategies 3 and 4 on a $\sim$3 hr baseline actually result in a large fraction of brightenings being undetectable.}
\label{fig:ch2_delm2}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f7.pdf}
\caption{Same as \Cref{fig:ch2_delm2}, except we plot the change in brightness between the first and third epoch $(\Delta m_{31})$ versus the brightness in the third epoch $(m_3)$. We find that the increased time between observations allows a much larger fraction of sources to exhibit a detectable change in brightness.}
\label{fig:ch2_delm3}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.9\textwidth]{./figs/chapter2/ch2_f8.pdf}
\caption{Simulated rise time-color phase-space for each of our four observing strategies. In each panel, we consider the full grid of kilonova models to a distance of 200 Mpc (orange). Each row highlights a different subset of the contaminant population over the comoving volume to $z_{\text{max}}$ (blue). The offset bins for Strategies 3 and 4 are due to the availability of intra-night observations on the first night. We find that the kilonovae are much redder than any potential contaminant, but the separation is less well-defined when compared to the light curves used in \cref{sec:ch2_phase}.}
\label{fig:ch2_mcphasecol}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.95\textwidth]{./figs/chapter2/ch2_f9.pdf}
\caption{Same as \Cref{fig:ch2_mcphasecol}, but showing the simulated rise time-$\Delta m_z$ slice of the phase-space. In this slice, there is much more confusion between the kilonovae and contaminant populations. With the exception of Type Ia SNe, there is significant overlap between kilonovae and the contaminant populations. This is the result of considering rapidly evolving sources for our contaminants, and it highlights the importance of color information in the selection of kilonovae candidates.}
\label{fig:ch2_mcphasedm}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f10.pdf}
\caption{The decline time-color slice of the decline time-color-magnitude phase-space. The plot is constructed using the same methodology as in \Cref{fig:ch2_mcphasecol,fig:ch2_mcphasedm}. We note that, as before, kilonovae show redder $i-z$ colors than the contaminant population. However, there is no strong separation in decline time.}
\label{fig:ch2_deccol}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.95\textwidth]{./figs/chapter2/ch2_f11.pdf}
\caption{The decline time-$\Delta m_z$ slice of the decline time-color-magnitude phase-space. The slow decline of Type Ia SNe and the Pan-STARRS fast transients separate them from the rapidly evolving kilonovae. However, the type .Ia and the miscellaneous fast transients show changes in brightness comparable to those of kilonovae.}
\label{fig:ch2_decdm}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.95\textwidth]{./figs/chapter2/ch2_f12.pdf}
\caption{Contours showing the fraction of kilonovae detected as a function of start time and depth for our four observing strategies and three filters when a pre-existing template is not available. We first note that $i$- and $z$-band observations in this scenario must be $\sim1$ mag deeper to achieve detection rates comparable to when a pre-existing template is available. We also note an effect in {\em z}-band where the 95\% contour drops by $\sim1$ mag for observations starting between 6 and 12 hours after trigger using Strategy 2 and for observations starting less than 12 hours after the trigger using Strategy 4. This is the result of the observations straddling the peak of the light curve where the difference in flux between epochs is too small to detect.}
\label{fig:ch2_detdiff}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f13.pdf}
\caption{Same as \Cref{fig:ch2_detdiff}, but showing the fraction of sources for which brightening is detected. We note that when compared to the contours shown in \Cref{fig:ch2_rise} for the case of a pre-existing template, observations must go deeper in this scenario and the detection efficiency quickly tapers off as a function of starting time. This highlights the importance of commencing follow-up observations as soon as possible when a pre-existing template is not available.}
\label{fig:ch2_risediff}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.95\textwidth]{./figs/chapter2/ch2_f14.pdf}
\caption{The rise time-color slice of our phase-space when a pre-existing template is not available. We note that if the rise time is long ($\gtrsim2$ days), then there is sufficient evolution in the light curve that colors can be measured with reasonable accuracy and kilonovae can be separated from the contaminants as before. However, when the rise time is short $(\sim 1$ day), then the change in flux is small and the colors are not well constrained.}
\label{fig:ch2_phaserisediff}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f15.pdf}
\caption{The rise time-$m^{\star}_z$ slice of our phase-space. The slower evolution of Type Ia SNe is apparent. For the remaining contaminants the observed change in flux is comparable to that observed for kilonovae. The rise times exhibited by both the kilonovae and contaminant populations are also comparable, however only contaminants show a rise time $\gtrsim 5$ days.}
\label{fig:ch2_phaserisediff_df}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f16.pdf}
\caption{Same as \Cref{fig:ch2_phaserisediff} but showing the decline time-color slice of the phase-space. The kilonovae are not always clearly separated from the contaminant population due to the imprecise color measurements. However, contaminants (with the exception of the miscellaneous fast transients) do stand out from kilonovae on the basis of their long decline times ($\gtrsim 6$ days, the maximal length given our search duration).}
\label{fig:ch2_phasedecdiff}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f17.pdf}
\caption{Same as \Cref{fig:ch2_phaserisediff_df} but showing the decline time-$m^{\star}_z$ slice of the phase-space. As in \Cref{fig:ch2_phaserisediff_df}, the contaminants are not clearly separated from the kilonovae population in $m^{\star}_z$. However, as in \Cref{fig:ch2_phasedecdiff}, the long decline times can be used to distinguish kilonovae from the contaminant populations.}
\label{fig:ch2_phasedecdiff_df}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f18.pdf}
\caption{{\em r}-band light curves from the alternative kilonova models discussed in \cref{sec:ch2_HMNS,sec:ch2_neutronpre}. The {\em r}-band light curve for the neutron-rich dynamical ejecta with $M_{{\rm ej}} = 10^{-2}\;M_{\odot}$ and $\beta_{{\rm ej}} = 0.2$ is plotted for comparison. The alternative models produce light curves which can be significantly brighter and bluer than the dynamical ejecta but peak at earlier times.}
\label{fig:ch2_altLC}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f19.pdf}
\caption{Contour plots for the {\em r}-band detectability of alternative kilonovae models. The top row shows the contours for the dynamical ejecta (reproduced from \cref{sec:ch2_MCsims_det}). The middle row shows contours for a long-lived HMNS with a lifetime of $\sim 100$ ms, surrounded by a dynamical tours with a mass of $10^{-2}\;M_{\odot}$  of neutron-rich material observed at a viewing angle of $\theta \sim 18$ deg as modeled by \citet{Kasen+15}. The bottom row shows the effect of an early-time neutron precursor as modeled by \citet{Metzger+15}.}
\label{fig:ch2_altdet}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f20.pdf}
\caption{Same as \Cref{fig:ch2_altdet}, but showing the fraction of events for which a brightening is detected. Compared to the case of dynamical ejecta only, it is significantly more challenging to detect brightening in these alternative kilonova models due to their earlier peak times and rapid evolution.}
\label{fig:ch2_altrise}
\end{figure}

>>>>

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f1.pdf}
\caption{ \singlespace Top: Kilonova spectra from \citet{BarnesKasen13} at $\sim$ 1 d and $\sim$ 1 week with ejecta properties of $\Mej =10^{-2}\;M_{\odot}$ and $\beta_{\text{ej}} = 0.2$. Bottom: Light curve for the same model parameters computed at a fiducial distance of 200 Mpc in the DECam {\em r}, {\em i}- and {\em z}-band filters. \vspace{10pt}}
\label{fig:ch2_kilosample}
\end{figure}

@@

\clearpage
\begin{figure}[h!]
\centering
\includegraphics[width=0.65\textwidth]{./figs/chapter2/ch2_f2.pdf}
\caption{ \singlespace Top: {\em i}-band light curves of the contaminants considered in this work at a fiducial distance of 200 Mpc. Bottom: {\em z}-band light curves. See \cref{sec:ch2_WDmerge,sec:ch2_AIC,sec:ch2_ELDD,sec:ch2_type.Ia,sec:ch2_PSFast,sec:ch2_typeIa} for details.}
\label{fig:ch2_LCcont}
\end{figure}

@@

\clearpage
\singlespace
\begin{deluxetable}{cccccc}
\tabletypesize{\footnotesize}
\tablecolumns{6}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Expected Rates For Fast Transients}
\tablehead{
\colhead{Object}&  \colhead{$\mathcal{R}_{\rm vol}$}& \colhead{$z_{\rm max}$}  &  \colhead{$\mathcal{R}_{\rm area}$} &  \colhead{$N$}     &     \colhead{Reference}      \\
\colhead{} & \colhead{(Mpc$^{-3}$ yr$^{-1}$)} & \colhead{} & \colhead{(deg$^{-2}$ yr$^{-1}$)} &  \colhead{} & \colhead{} }
\startdata
 Type .Ia    &                  10$^{-6}$                   &  0.5        &  $0.7$            &         1.4  & \citet{Bildsten+07} \\
 WD-NS mergers  &                  10$^{-5}$                   &   0.06        & $2\times10^{-2}$              &         $3\times10^{-2}$  &     \citet{Thompson+09}     \\
 WD-BH mergers  &      10$^{-5}$                   &    0.06        &   $2\times10^{-2}$              &      $3\times10^{-2}$  &    \citet{Fryer+99}          \\
AIC       &                  10$^{-6}$                   & 0.06        & $2\times10^{-3}$            &        $3\times10^{-3}$ &  \citet{Darbha+10}   \\
ELDD      &                  3$\times 10^{-7}$                   & 0.14        &    $6\times10^{-3}$           &      $1\times10^{-2}$ &  $\cdots$  \\
Pan-STARRS fast &                  5$\times 10^{-6}$                   &     0.5        &   $3.5$            &     7 &   \citet{Drout+14}
\enddata
\tablecomments{Expected rates for the various contaminants considered in \cref{sec:ch2_contaminants}. $\mathcal{R}_{\rm area}$ is computed assuming an isotropic distribution of sources in a volume defined by the comoving volume at $z_{\rm max}$.  The column $N$ refers to the number of events expected during a search covering 100 deg$^2$ for 7 days. See \cref{sec:ch2_rates} or details.}
\label{tab:ch2_rates}
\end{deluxetable}

@@

\clearpage
\doublespace 
To estimate the expected number of events observed during a GW optical follow-up search we compute the number of sources per square degree per year. This is done by determining the maximum redshift to which the object can be observed to a limiting magnitude of $z \approx$ 23 mag (see \cref{sec:ch2_kilo,sec:ch2_MCsims_det}). This rate is then multiplied by the search area $(A \sim 100$ deg$^2$) and duration to get the number of expected sources for our observations. We compute the duration by assuming that a kilonova will be detected within approximately one day of the GW trigger. Therefore, we do not consider events that begin more than +2 d into the search. However, we do consider sources that begin up to twice their characteristic timescale ($\sim5$ d for rapid transients and $\sim 20$ d for Type Ia SNe) prior to the GW trigger, as they may remain visible when the search begins. The total duration is then 7 d for rapid transients and 22 d for Type Ia SNe. The number of expected sources is given in \cref{tab:ch2_rates,tab:ch2_rates_Iae}. Type Ia SNe dominate the number of expected events with $N \sim 568$ when summing across all redshift bins. Of the population of fast transients, only type .Ia and the Pan-STARRS fast transients are expected to have $N \gtrsim 1$. Despite the low expected occurrence rate for other fast transients, we still consider these sources in this analysis due to the large uncertainty in their rates.

@@

\begin{figure*}[t!]
\centering
\includegraphics[trim= 0 0 0 250 ,clip,width=\textwidth]{./figs/chapter2/ch2_f3.pdf}
\caption{ \singlespace Time-color (left) and time-magnitude (right) slices of the time-color-magnitude phase-space at a selection of redshifts. Arrow markers denote upper limits on the rise time. Note that in all panels the population of kilonovae are kept at the fiducial distance of $\sim$ 200 Mpc while redshift corrections are applied to the contaminant population. Kilonovae are well separated from the contaminant population in both color and timescales. The delineation in magnitude is less apparent.}
\label{fig:ch2_phase}
\end{figure*}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f4.pdf}
\caption{ \singlespace Depth versus start time grid in $r$ (top), $i$ (middle), and $z$ (bottom) for the four observing strategies. The contours indicate the fraction of sources detected in at least three epochs (25\% blue, 50\% cyan, 75\% yellow, 95\% red). The dashed lines represent the approximate 5$\sigma$ limiting magnitudes of several wide-field telescopes assuming the appropriate number of pointings necessary to cover a $\sim 100$ deg$^2$ error region with the required cadence. The choice of observing strategy does not drastically affect the fraction of sources detected at a given depth. We note that the early time drop in efficiency for {\em z}-band utilizing Strategy 2 is the result of the initial observations occurring before the light curve has brightened above the limiting magnitude.}
\label{fig:ch2_det}
\end{figure}

@@

\clearpage
\begin{landscape}
\singlespace
\begin{deluxetable}{ccccc|cccc}
\tabletypesize{\footnotesize}
\tablecolumns{9}
\tabcolsep0.05in\footnotesize
\tablewidth{0pt}
\tablecaption{Required 5$\sigma$ Limiting Magnitudes for Kilonova Detection}
\tablehead{\colhead{Filter} & \multicolumn{4}{c|}{With Pre-Existing Template} & \multicolumn{4}{c}{Without Pre-Existing Template} \\
\colhead{} & \colhead{Strategy \#1} & \colhead{Strategy \#2} & \colhead{Strategy \#3} & \multicolumn{1}{c|}{Strategy \#4} & \colhead{Strategy \#1} & \colhead{Strategy \#2} & \colhead{Strategy \#3} & \colhead{Strategy \#4}}
\startdata
$r$ & 24.9 (25.9) & 25.0 (25.9) & 24.5 (25.5) & 24.5 (25.5) & 25.0 (25.9) & 25.0 (25.9) & 25.0 (25.9) & 25.1 (25.9) \\
$i$ & 23.2 (23.9) & 23.3 (24.0) & 22.9 (23.9) & 22.9 (23.9) & 24.0 (24.9) & 24.3 (25.0) & 24.0 (24.9) & 24.3 (25.0) \\
$z$ & 22.2 (22.9) & 22.4 (23.2) & 22.1 (22.9) & 22.1 (23.0) & 23.1 (23.9) & 23.2 (24.0) & 23.1 (23.9) & 23.5 (24.2)
\enddata
\tablecomments{\,Limiting magnitudes $(5\sigma)$ required to detect 50\% (95\%) of kilonovae as a function of observing strategy and filter (\cref{sec:ch2_MCsims_det}, \Cref{fig:ch2_det}). Values are averaged over all start times. We compute the required depths for follow-up observations with and without a pre-existing template (\cref{sec:ch2_diff}).}
\label{tab:ch2_det}
\end{deluxetable}
\end{landscape}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f5.pdf}
\caption{ \singlespace Same as \Cref{fig:ch2_det}, except that the contours show the fraction of events for which a brightening is detected. The choice of observing strategy, start time, and filter have a strong impact on the detection of brightening.}
\label{fig:ch2_rise}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f6.pdf}
\caption{ \singlespace Probability density of kilonovae as a function of the change in brightness between the first and second observation $(\Delta m_21)$ versus the brightness in the second observation $(m_2)$ for each of the four observing strategies. The hatched region indicates the $2\sigma$ photometric error for DECam for an exposure time necessary to achieve the required depth. Points within this region will not exhibit a statistically significant change in magnitude for detection. The fraction of sources brighter than the detection limit in all three observations (DF) and the fraction of sources within the hatched region (missed) are indicated at the bottom of each panel. We find that the seemingly beneficial initial rapid cadence of Strategies 3 and 4 on a $\sim$3 hr baseline actually result in a large fraction of brightenings being undetectable.}
\label{fig:ch2_delm2}
\end{figure}

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f7.pdf}
\caption{ \singlespace Same as \Cref{fig:ch2_delm2}, except we plot the change in brightness between the first and third epoch $(\Delta m_{31})$ versus the brightness in the third epoch $(m_3)$. We find that the increased time between observations allows a much larger fraction of sources to exhibit a detectable change in brightness.}
\label{fig:ch2_delm3}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.9\textwidth]{./figs/chapter2/ch2_f8.pdf}
\caption{ \singlespace Simulated rise time-color phase-space for each of our four observing strategies. In each panel, we consider the full grid of kilonova models to a distance of 200 Mpc (orange). Each row highlights a different subset of the contaminant population over the comoving volume to $z_{\text{max}}$ (blue). The offset bins for Strategies 3 and 4 are due to the availability of intra-night observations on the first night. We find that the kilonovae are much redder than any potential contaminant, but the separation is less well-defined when compared to the light curves used in \cref{sec:ch2_phase}.}
\label{fig:ch2_mcphasecol}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.95\textwidth]{./figs/chapter2/ch2_f9.pdf}
\caption{ \singlespace Same as \Cref{fig:ch2_mcphasecol}, but showing the simulated rise time-$\Delta m_z$ slice of the phase-space. In this slice, there is much more confusion between the kilonovae and contaminant populations. With the exception of Type Ia SNe, there is significant overlap between kilonovae and the contaminant populations. This is the result of considering rapidly evolving sources for our contaminants, and it highlights the importance of color information in the selection of kilonovae candidates.}
\label{fig:ch2_mcphasedm}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f10.pdf}
\caption{ \singlespace The decline time-color slice of the decline time-color-magnitude phase-space. The plot is constructed using the same methodology as in \Cref{fig:ch2_mcphasecol,fig:ch2_mcphasedm}. We note that, as before, kilonovae show redder $i-z$ colors than the contaminant population. However, there is no strong separation in decline time.}
\label{fig:ch2_deccol}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.95\textwidth]{./figs/chapter2/ch2_f11.pdf}
\caption{ \singlespace The decline time-$\Delta m_z$ slice of the decline time-color-magnitude phase-space. The slow decline of Type Ia SNe and the Pan-STARRS fast transients separate them from the rapidly evolving kilonovae. However, the type .Ia and the miscellaneous fast transients show changes in brightness comparable to those of kilonovae.}
\label{fig:ch2_decdm}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.95\textwidth]{./figs/chapter2/ch2_f12.pdf}
\caption{ \singlespace Contours showing the fraction of kilonovae detected as a function of start time and depth for our four observing strategies and three filters when a pre-existing template is not available. We first note that $i$- and $z$-band observations in this scenario must be $\sim1$ mag deeper to achieve detection rates comparable to when a pre-existing template is available. We also note an effect in {\em z}-band where the 95\% contour drops by $\sim1$ mag for observations starting between 6 and 12 hours after trigger using Strategy 2 and for observations starting less than 12 hours after the trigger using Strategy 4. This is the result of the observations straddling the peak of the light curve where the difference in flux between epochs is too small to detect.}
\label{fig:ch2_detdiff}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f13.pdf}
\caption{ \singlespace Same as \Cref{fig:ch2_detdiff}, but showing the fraction of sources for which brightening is detected. We note that when compared to the contours shown in \Cref{fig:ch2_rise} for the case of a pre-existing template, observations must go deeper in this scenario and the detection efficiency quickly tapers off as a function of starting time. This highlights the importance of commencing follow-up observations as soon as possible when a pre-existing template is not available.}
\label{fig:ch2_risediff}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=0.95\textwidth]{./figs/chapter2/ch2_f14.pdf}
\caption{ \singlespace The rise time-color slice of our phase-space when a pre-existing template is not available. We note that if the rise time is long ($\gtrsim2$ days), then there is sufficient evolution in the light curve that colors can be measured with reasonable accuracy and kilonovae can be separated from the contaminants as before. However, when the rise time is short $(\sim 1$ day), then the change in flux is small and the colors are not well constrained.}
\label{fig:ch2_phaserisediff}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f15.pdf}
\caption{ \singlespace The rise time-$m^{\star}_z$ slice of our phase-space. The slower evolution of Type Ia SNe is apparent. For the remaining contaminants the observed change in flux is comparable to that observed for kilonovae. The rise times exhibited by both the kilonovae and contaminant populations are also comparable, however only contaminants show a rise time $\gtrsim 5$ days.}
\label{fig:ch2_phaserisediff_df}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f16.pdf}
\caption{ \singlespace Same as \Cref{fig:ch2_phaserisediff} but showing the decline time-color slice of the phase-space. The kilonovae are not always clearly separated from the contaminant population due to the imprecise color measurements. However, contaminants (with the exception of the miscellaneous fast transients) do stand out from kilonovae on the basis of their long decline times ($\gtrsim 6$ days, the maximal length given our search duration).}
\label{fig:ch2_phasedecdiff}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f17.pdf}
\caption{ \singlespace Same as \Cref{fig:ch2_phaserisediff_df} but showing the decline time-$m^{\star}_z$ slice of the phase-space. As in \Cref{fig:ch2_phaserisediff_df}, the contaminants are not clearly separated from the kilonovae population in $m^{\star}_z$. However, as in \Cref{fig:ch2_phasedecdiff}, the long decline times can be used to distinguish kilonovae from the contaminant populations.}
\label{fig:ch2_phasedecdiff_df}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f18.pdf}
\caption{ \singlespace {\em r}-band light curves from the alternative kilonova models discussed in \cref{sec:ch2_HMNS,sec:ch2_neutronpre}. The {\em r}-band light curve for the neutron-rich dynamical ejecta with $M_{{\rm ej}} = 10^{-2}\;M_{\odot}$ and $\beta_{{\rm ej}} = 0.2$ is plotted for comparison. The alternative models produce light curves which can be significantly brighter and bluer than the dynamical ejecta but peak at earlier times.}
\label{fig:ch2_altLC}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f19.pdf}
\caption{ \singlespace Contour plots for the {\em r}-band detectability of alternative kilonovae models. The top row shows the contours for the dynamical ejecta (reproduced from \cref{sec:ch2_MCsims_det}). The middle row shows contours for a long-lived HMNS with a lifetime of $\sim 100$ ms, surrounded by a dynamical tours with a mass of $10^{-2}\;M_{\odot}$  of neutron-rich material observed at a viewing angle of $\theta \sim 18$ deg as modeled by \citet{Kasen+15}. The bottom row shows the effect of an early-time neutron precursor as modeled by \citet{Metzger+15}.}
\label{fig:ch2_altdet}
\end{figure}

@@

\begin{figure}[t!]
\centering
\includegraphics[width=\textwidth]{./figs/chapter2/ch2_f20.pdf}
\caption{ \singlespace Same as \Cref{fig:ch2_altdet}, but showing the fraction of events for which a brightening is detected. Compared to the case of dynamical ejecta only, it is significantly more challenging to detect brightening in these alternative kilonova models due to their earlier peak times and rapid evolution.}
\label{fig:ch2_altrise}
\end{figure}
